---
title: "Presentation Outline AARUG AI in RStudio Meeting February 12, 2026"
author: "Barry DeCicco"
date: "2026-02-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## AI in R Programming

### Several AI tools are available to assist with R programming, including:
- ChatGPT from OpenAI,

- Microsoft Copilot,

- Posit Assistant (formerly RStudio Assistant),

- ClaudeAI from Anthropic,

- Github Copilot,

....and many others.

## Advantages

- These tools can help you write code faster, debug errors, and learn new techniques.

- They can also assist with data analysis, visualization, and even writing reports.

- They can help with debugging and troubleshooting code, which can save you time and frustration.

- They can help with language translation.

## Disadvantages

- These tools are not perfect and can sometimes generate incorrect or suboptimal code.

- They may not always understand the context of your project or the specific requirements of your code.

- They may not be able to handle complex or specialized tasks that require deep domain knowledge.

- They can generate overly complex code, which even skilled people can't.  understand, and which may be difficult to maintain or debug in the future.

- They can be *extremely* sensitive to the exact language of prompts;
similar prompts can yield very different results.

- They can also 'circle the block', iterating between two versions with the same 
error message (I haven't seen this mentioned in the literature, but I have seen it happen in practice). This will happen until the user stops.


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
