---
title: "Presentation Outline AARUG AI in RStudio Meeting February 12, 2026"
author: "Barry DeCicco"
date: "2026-02-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## AI in R Programming

## Several AI tools are available to assist with R programming, including:
- ChatGPT from OpenAI,

- Microsoft Copilot,

- Posit Assistant (formerly RStudio Assistant),

- ClaudeAI from Anthropic,

- Github Copilot,

....and many others.

### Advantages

- These tools can help you write code faster, debug errors, and learn new techniques.

- They can also assist with data analysis, visualization, and even writing reports.

- They can help with debugging and troubleshooting code, which can save you time and frustration.

- They can help with language translation.

### Disadvantages

- These tools are not perfect and can sometimes generate incorrect or suboptimal code.

- They may not always understand the context of your project or the specific requirements of your code.

- They may not be able to handle complex or specialized tasks that require deep domain knowledge.

- They can generate overly complex code, which even skilled people can't.  understand, and which may be difficult to maintain or debug in the future.

- They can be *extremely* sensitive to the exact language of prompts;
similar prompts can yield very different results.

- They can also 'circle the block', iterating between two versions with the same 
error message (I haven't seen this mentioned in the literature, but I have seen it happen in practice). This will happen until the user stops.

## My Rankings

1. Posit Assistant (formerly RStudio Assistant) - This tool is specifically designed for R programming and integrates well with RStudio. It provides helpful suggestions and can assist with a wide range of tasks, from writing code to debugging and learning new techniques.  **it is one the best pieces of software I've ever 
worked with!**  This is also in Beta testing.

2. Claude AI (Anthropic) - this was the easiest to use, with good results and 
easy iteration and good integration with RStudio. It is a general-purpose AI, but it performed well with R programming tasks.

3. Microsoft Copilot - this tool is integrated with Microsoft products and can assist with coding tasks; but it may not be as specialized for R programming as Posit Assistant (like Claude AI), but works similarly.

4. Github Copilot - this is build into Github, VS Code and Rstudio. The big
drawback is that it has line by line completion (suggest a line, hit tab to 
accept that line, hit return, repeat). This can be tedious for long piece of 
code.

5. ChatGPT (OpenAI) - I found this difficult to integrate into RStudio.


## Example - Github Copilot

This is enabled by selecting Tools > Global Options > Copilot and checking 
'Enable Github Copilot'.  You might have to sign in to Github.

At that point, if you start a line with a single '#', Github Copilot will 
suggest something; if you hit 'tab', this will be accepted, and chnage from
gray to block.

I do not know which model is active in Github Copilot; a Google search suggests
that users can not find this out.

[Demonstrate]


## Example - Claude AI

Claude AI performed very well.  It iterates nicely, meaning that it will:
explain what it's doing, produce code, accept corrective prompts, make
and explain changes.  It will keep printing out the process in a web page,
which you can save, and revisit through the URL.  It has a sidebar to make
it easier to navigate the process.

Demonstrate with [saved Claude AI session](https://claude.ai/chat/5051870e-9ba8-429f-94e6-837777907a21)
 



```{r cars}
summary(cars)
```
















