---
title: "Presentation Outline AARUG AI in RStudio Meeting February 12, 2026"
author: "Barry DeCicco"
date: "2026-02-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## AI in R Programming

### Several AI tools are available to assist with R programming, including:
- ChatGPT from OpenAI,
- Microsoft Copilot,
- Posit Assistant (formerly RStudio Assistant),
- ClaudeAI from Anthropic,
- Github Copilot,
and many others.

## Advantages

- These tools can help you write code faster, debug errors, and learn new techniques.
- They can also assist with data analysis, visualization, and even writing reports.
- They can help with debugging and troubleshooting code, which can save you time and frustration.
- They can help with language translation.

## Disadvantages




```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
